Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-10-16 doc/Paper/main.tex
Started cleaning up notation confusion for HOD parameters.

    We expect mean galaxy properties to evolve as a function of redshift for the magnitude-limited sample considered in this analysis. Instead of fitting a separate HOD model to each redshift bin, we fit redshift-dependent functions to $M_{\mathrm{min}}$, $M_{0}$ and $M_{1}$ and choose a functional form given by:
    \begin{equation}
      M_{i}(z) = M_{i} + M_{i, p} \left(\frac{1}{1+z} - \frac{1}{1+z_{p}}\right),
    \end{equation}
    where $i \in [\mathrm{min}, 0, 1]$ and $z_{p}$ denotes a pivot redshift, which we set to $z_{p} = 0.65$. This functional form is motivated by an initial analysis in which we separately fit an HOD to each auto power spectrum and determine a function consistent with the observed redshift evolution of the three parameters $M_{\mathrm{min}}$, $M_{0}$ and $M_{1}$. We additionally include a pivot redshift $z_{p}$ in our parametrization to remove degeneracies between the fitted parameters.

@@

Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}. The constraints on all fitted parameters are shown in Fig.~\ref{fig:constraints-fid-full} and the corresponding best-fit values and means are shown alongside their $68 \%$ confidence limits in Tab.~\ref{tab:params}. As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$.} \todo{explain upper bound}. Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters together with our the measured power spectra. The corresponding minimum $\chi^{2}$ is $\chi^{2} = 86.2$. Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.08$ ($p$-value $= 0.30$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g. \cite{Andrae:2010}). However, we will use it throughout this work, as it allows us to obtain a rough estimate of the goodness of fit of the different models considered in our analysis.}.

>>>>

    We expect mean galaxy properties to evolve as a function of redshift for the magnitude-limited sample considered in this analysis. Instead of fitting a separate HOD model to each redshift bin, we fit redshift-dependent functions to $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$ and choose a functional form given by:
    \begin{equation}
      \log{M_{i}(z)} = M_{i} + M_{i, p} \left(\frac{1}{1+z} - \frac{1}{1+z_{p}}\right),
    \end{equation}
    where $\log$ is the logarithm to base 10, $i \in [\mathrm{min}, 0, 1]$ and $z_{p}$ denotes a pivot redshift, which we set to $z_{p} = 0.65$. This functional form is motivated by an initial analysis in which we separately fit an HOD to each auto power spectrum and determine a function consistent with the observed redshift evolution of the three parameters $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$. We additionally include a pivot redshift $z_{p}$ in our parametrization to remove degeneracies between the fitted parameters.

@@

Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $M_{\mathrm{min}}, \allowbreak \, M_{\mathrm{min}, p}, \allowbreak \, M_{1}, \allowbreak \, M_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}. The constraints on all fitted parameters are shown in Fig.~\ref{fig:constraints-fid-full} and the corresponding best-fit values and means are shown alongside their $68 \%$ confidence limits in Tab.~\ref{tab:params}. As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$.} \todo{explain upper bound}. Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters together with our the measured power spectra. The corresponding minimum $\chi^{2}$ is $\chi^{2} = 86.2$. Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.08$ ($p$-value $= 0.30$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g. \cite{Andrae:2010}). However, we will use it throughout this work, as it allows us to obtain a rough estimate of the goodness of fit of the different models considered in our analysis.}.
